---
title: "Food Preference Survey"
output: html_notebook
---

# Food Preference Survey

##### This Survey was conducted among participants from different countries and demography. This will enable the resturant know the popularity of the food type among their residence at the resort.

```{r}
# Installing required libraries

install.packages("tidyverse")
install.packages("dplyr")
install.packages("tidyr")
install.packages("ggplot2")
install.packages("gridExtra")
install.packages("readr")
install.packages("skimr")
install.packages("caret")
install.packages("e1071")
```

```{r}
# Importing Libraries 

library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)

# Data Importation:
library(readr)

# Summaries of Data:
library(skimr)

# Predictive Modeling/ML:
library(caret)
library(e1071)
```

```{r}
food_survey <- read_csv("Food_survey.csv")
```
## Data Cleaning
```{r}
# Checking the provided sections
str(food_survey)
```

```{r}
# Check for duplicate Participant_IDs:
sum(duplicated(food_survey$Participant_ID) == TRUE)
```
No duplicate Participant_IDs are present.
```{r}
# Delete Participant_ID column and Timestamp columns; they are unneeded.
food_survey <- select(food_survey, -Timestamp)
food_survey <- select(food_survey, -Participant_ID)
head(food_survey)
```

```{r}
skim(food_survey)
```
The Gender column contains 4 NA entries, according to the summary. 
Lets check to see which rows in the dataframe contain NAs:
```{r}
food_survey[!complete.cases(food_survey),]
```
This confirms that all the NAs are in the Gender column. Lets Delete the rows containing NAs:
```{r}
food_survey <- na.omit(food_survey)
```

```{r}
# See which Nationalities are represented:
as.matrix(unique(food_survey$Nationality))
```
Some of the names in the Nationality column are misspelled or otherwise inconsistent.

Let's make them consistent:
```{r}
# Nationality - Malaysian 
food_survey$Nationality <- gsub("Malaysia", "Malaysian", food_survey$Nationality)
food_survey$Nationality <- gsub("MALAYSIAN", "Malaysian", food_survey$Nationality)
food_survey$Nationality <- gsub("Malaysiann", "Malaysian", food_survey$Nationality)
food_survey$Nationality <- gsub("MY", "Malaysian", food_survey$Nationality)
# Nationality - Indonesian
food_survey$Nationality <- gsub("Indonesain", "Indonesian", food_survey$Nationality)
food_survey$Nationality <- gsub("Indonesia", "Indonesian", food_survey$Nationality)
food_survey$Nationality <- gsub("Indonesiann", "Indonesian", food_survey$Nationality)
# Nationality - Pakistani
food_survey$Nationality <- gsub("Pakistan", "Pakistani", food_survey$Nationality)
food_survey$Nationality <- gsub("Pakistanii", "Pakistani", food_survey$Nationality)
```

```{r}
as.matrix(unique(food_survey$Nationality))
```
Getting the count of all the nationality
```{r}
food_survey %>% count(Nationality, sort = TRUE)
```
Very few of the records correspond to non-Indian nationalities. Due to the severe class imbalance, we can consolidate these other nationalities into a single 'Non_Indian' class.


## Data Visualization EDA
```{r}
## Let's graph the totals for the other categorical variables:

food_survey %>% count(Food, sort = TRUE) -> Food_count
Food_count %>% ggplot(aes(x = Food, y = n)) + geom_bar(stat = "identity") + geom_bar(stat = "identity", color = "#E69F00", fill = "#E69F00") + geom_text(aes(label=n), color="white", fontface = "bold", vjust = 1.5, size=5) -> Food_count_g

food_survey %>% count(Juice, sort = TRUE) -> Juice_count
Juice_count %>% ggplot(aes(x = Juice, y = n)) + geom_bar(stat = "identity") + geom_bar(stat = "identity", color = "#56B4E9", fill = "#56B4E9") + geom_text(aes(label=n), color="white", fontface = "bold", vjust = 1.5, size=5) -> Juice_count_g

food_survey %>% count(Dessert, sort = TRUE) -> Dessert_count
Dessert_count %>% ggplot(aes(x = Dessert, y = n)) + geom_bar(stat = "identity") + geom_bar(stat = "identity", color = "#FF6433", fill = "#FF6433") + geom_text(aes(label=n), color="white", fontface = "bold", vjust = 1.5, size=5) -> Dessert_count_g

food_survey %>% count(Gender, sort = TRUE) -> Gender_count
Gender_count %>% ggplot(aes(x = Gender, y = n)) + geom_bar(stat = "identity", color = "#2BD64D", fill = "#2BD64D") + geom_text(aes(label=n), color="white", fontface = "bold", vjust = 1.5, size=5) -> Gender_count_g

grid.arrange(Food_count_g, Juice_count_g, Dessert_count_g, Gender_count_g)
```
Lets see if  Dessert more or less popular in the context of certain Food and Juice preferences? Let's examine normalized dessert data
```{r}
summary1 <- food_survey %>%
        count(Food, Juice, Dessert, sort = TRUE)

ggplot(summary1, aes(Juice, n, fill = Dessert)) + 
        geom_bar(position = "fill" , stat = "identity", color = "black") +
        facet_wrap(facets = vars(Food)) +
        scale_fill_brewer(palette = "Accent") +
        theme_bw() + scale_y_continuous(labels = scales::percent) +
        ggtitle("Relative Popularity of Dessert per Food and Juice Preference") +
       labs(y = NULL)

#Try this if u need to add new colors
#scale_fill_manual(values = c("#56B4E9", "#736F6E", "#FF6433", "#2BD64D"))

#https://htmlcolorcodes.com/  --> to find manual good colors
# http://rstudio-pubs-static.s3.amazonaws.com/5312_98fc1aba2d5740dd849a5ab797cc2c8d.html ---> Check for coloring 
```

Convert Categorical Variable to Numeric

```{r}


foodsur_m <- food_survey

foodsur_m <- food_survey %>%
        filter(Dessert == c("Yes", "No")) %>%
        mutate_if(is.character, stringr::str_replace_all, pattern = 'Yes', replacement = 'Yes') %>% 
        mutate_if(is.character, stringr::str_replace_all, pattern = 'No', replacement = 'No')

foodsur_m <- foodsur_m %>%
mutate(across(where(is.character), as.factor),
      across(where(is.factor), as.numeric),
      Dessert = factor(ifelse(Dessert == 0, "No", "Yes")))
head(foodsur_m)
```

```{r}
# Barplot
bp<- ggplot(food_survey, aes(x="", y=Gender, fill=Nationality))+
geom_bar(width = 1, stat = "identity")
pie <- bp + coord_polar("y", start=0)
pie + scale_fill_brewer(palette="Blues")+
  theme_minimal()
```

```{r}
res = cor(foodsur_m[,c(1,2,3,5)])
res
```

```{r}
# Histogram combines the dots, and the y axis now shows the actual count
ggplot(foodsur_m,aes(x=Age)) + geom_histogram()
```
Heatmapping the median ages for each preference:

```{r}
food_surheatmap1 <- ggplot(data = food_survey, mapping = aes(x = Juice,
                                                       y = Gender,
                                                       fill = Age)) +
  geom_tile() +
  xlab(label = "Juice Preferance based on Gender and Median Age")

food_surheatmap2 <- ggplot(data = food_survey, mapping = aes(x = Dessert,
                                                       y = Gender,
                                                       fill = Age)) +
  geom_tile() +
  xlab(label = "Dessert Preferance based on Gender and Median Age")


food_surheatmap1


```

```{r}
food_surheatmap2
```

